IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-07 paper/extensions.tex
scheduling

\subsection{Scheduling Policies}
Our specification language is parametrized by a scheduling policy
|alpha|, which maps a task list to a potentially different task list.
%
As previously discussed, the precise definition of |alpha|
dictates whether the language is TSNI, TINI, or neither.
%
For simplicity we considered two popular policies |roundrobinf| and
|seqf| for which we showed TSNI and TINI, respectively.
%
However, our definitions allow for other scheduling policies that only
rely on the current task list.
%
For example, this allows us to implement the scheduler of~\cite{Kashyap:2011}
that always schedules less sensitive threads first; this can be
employed to address external timing covert channels where an attacker
can measure the delay between output events.\footnote{
  When considering a label lattice that is not totally ordered, e.g.,
  DCLabels~\cite{myers:dlm,dclabels}, this scheduling policy is
  considerably more complex. See~\cite{Kashyap:2011}.
}
%
More generally, we believe that deterministic schedulers that always
make ``low-progress,'' i.e., if a task whose label is not above the
current task's label will will eventually run, and do not decide which
low tasks to schedule according to data more sensitive than the tasks'
label, i.e., the scheduler does not schedule one public thread over
another according to sensitive data, to be safe.
%

Despite allowing a number of practical schedulers to be expressed, our
scheduler parametrization is limited.
%
For instance, since |alpha| is a map on task lists, schedulers that
rely on the global state |iS| or previous task configurations cannot
be expressed.
%
Though, we do not believe this to be a fundamental limitation, our
current formalization cannot directly be applied to more-powerful, but
safe, scheduling policies, as considered by~\cite{russo2006securing}.
%
More fundamentally, our definitions rely on deterministic relations,
and thus extending the system to consider non-deterministic schedulers
(or even non-deterministic target languages) is non-trivial.
%
For instance, this may potentially require the security condition to
consider \emph{low-determinism}, which states that a program is secure
only if |l|-equivalent results are deterministic~\cite{Zdancewic:Myers:CSFW03,
sabelfeld2003language}.

>>>>

\subsection{Scheduling Policies}
Our specification language is parametrized by a scheduling policy
|alpha|, which maps a task list to a potentially different task list.
%
As previously discussed, the precise definition of |alpha|
dictates whether the language is TSNI, TINI, or neither.
%
For simplicity we considered two popular policies |roundrobinf| and
|seqf| for which we showed TSNI and TINI, respectively.
%
However, our definitions allow for other scheduling policies that only
rely on the current task list.
%
For example, this allows us to implement the scheduler of~\cite{Kashyap:2011}
that always schedules less sensitive threads first; this can be
employed to address external timing covert channels where an attacker
can measure the delay between output events.\footnote{
  When considering a label lattice that is not totally ordered, e.g.,
  DLM~\cite{myers:dlm} or DCLabels~\cite{dclabels}, this scheduling policy is
  considerably more complex.
}
%
Our formalism generalizes to a class of stateless, deterministic
schedulers that are: 1) \emph{integrity-preserving}, i.e., they do not
modify (or create) tasks; 2) \emph{non-interfering at level |l|}, the
greatest lower bound of all the labels on the task labels,\footnote{
  The label on a task's current label is the current label of the
  parent at the time of creation, i.e., the initial current label of
  the task.
} i.e., they do not depends on a sensitive task's state; and, 3) make
\emph{low-progress}, i.e., if there is a task in the task list whose
label is below (or incomparable to) the label of another task, this
task (or another one at the same level) must eventually run.
%
The last condition is required for TSNI; languages relying on
schedulers, such as |seqf|, that do not satisfy the low-progress
condition can at most satisfy TINI.
%
For simplicity, we do treat this, more-general class of schedulers;
doing so would require modifying our calculus to keep track of the
label on the current label of tasks and complicate the
non-interference proofs.

More fundamentally, our scheduler parametrization is limited in being
stateless and deterministic.
%
For instance,  we do not consider  schedulers that, among other, rely
on the global state |iS| or previous task configurations, as treated
in~\cite{russo2006securing}.
%
Additionally, our definitions rely on deterministic relations,
and thus extending the system to consider non-deterministic schedulers
(or even non-deterministic target languages) is non-trivial.
%
Such extensions may potentially require the security condition to
consider \emph{low-determinism}, which states that a program is secure
only if |l|-equivalent results are
deterministic~\cite{Zdancewic:Myers:CSFW03, sabelfeld2003language}.
